---
title: "Who Does More Pushups"
author: "Jonathan Paul P Clavio"
date: "October 01, 2020"
output:
html_document:
number_sections: true
toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
data(pushups)
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Pushups is a numeric variable  
Position is categorical  
We will load the numerical~cat template  

$H_0$ The null hypothesis states that there is no difference in the average number of pushups players can do in two minutes based on the position they play.  

$H_A$ The alternative hypothesis states that there is a difference in the average number of pushups players can do in two minutes based on the position they play.  


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(pushups~position,data=pushups)
```

This graphic shows the categorical variables (linemen and skill players) and there relation on how much they can do pushups.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=pushups)
```

The numerical description shows that linemen do around 14-15 pushups in 2 minutes and that the skill players do around 47-48 pushups in 2 minutes.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=pushups)
```

T.Test shows that the P-Value is 0.000009421 < 0.05. Therefore there is a no true difference between linemen and skill players.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We used a T.Test because the catagorical variable has only two levels, line and skill positions.  
Based on the graphical and numerical results provided, the skill players did almost double the amount of pushups compared to the linemen players.  
The P-Value is smaller (0.000009421) than 0.05; therefore we reject the null hypothesis.  
We conclude that there is a difference between the linemen and skill players in the amount of pushups they can do in 2 minutes.  